### 2019-08-19 maciek.tex
Some fixes

\begin{theorem}
  The cost of rebalancing cost for algorithm is $O(k)$.
  \label{rebalancing-cost}
\end{theorem}

\begin{proof}
  \maciek{Note: we consider a cost of cheapest feasible rebalancing after insertion of one edge. This in contrast to bounding the distance between any two reconfigurations (we do not do that).}

>>>>

\begin{theorem}
  The rebalancing cost for the greedy algorithm is $O(k)$.
  \maciek{Greedy = find the cheapest feasible partition}
  \label{rebalancing-cost}
\end{theorem}

\begin{proof} 
 \maciek{Note: we consider a cost of cheapest feasible rebalancing after insertion of one edge. This in contrast to bounding the distance between any two reconfigurations (this theorem does not bound the latter).}
